Software Citation Principles

### 2016-02-24 sc-principles/software-citation-principles.tex
add note

\newcommand{\katznote}[1]{ {\textcolor{blue} { ***DSK: #1 }}}
\newcommand{\niemnote}[1]{ {\textcolor{orange} { ***KEN: #1 }}}
\newcommand{\asnote}[1]{ {\textcolor{red} { ***AMS: #1 }}}

@@

We have documented and analyzed a set of use cases related to software citation in \cite{SC-Use-Cases}.
Table~\ref{tab:use_cases} summarizes these use cases and makes clear what the requirements are for software citation in each case.
\katznote{not sure if this next long sentence should be here, should be in the table caption, or should be footnotes to the table, or even more than one of these}
\niemnote{Not sure either; definitely should include in the text due to length. Maybe an abbreviated version in the caption?}
In the table,
``researcher'' includes both academic researchers (e.g., postdoc, tenure-track faculty member) and research software engineers;
``publisher'' includes both traditional publishers that publish text and\slash or software papers as well as archives such as Zenodo that directly publish software;
``reproduce'' can mean reproduction, replication, verification, validation, repeatability, and\slash or utility;
examples of indexers include Scopus, Web of Science, Google Scholar, and Microsoft Academic Search;
domain groups include bioCADDIE, CIG, etc.;
``repository'' refers to open-source software repositories such as ASCL, GitHub, Netlib, CRAN, institutional repositories;
``funder'' is a group that funds software or work using software; and
``UID'' means unique ID, such as DOI or PURL.

>>>>

\newcommand{\katznote}[1]{ {\textcolor{blue} { ***DSK: #1 }}}
\newcommand{\niemnote}[1]{ {\textcolor{orange} { ***KEN: #1 }}}
\newcommand{\asnote}[1]{ {\textcolor{red} { ***AMS: #1 }}}
\newcommand{\flnote}[1]{ {\textcolor{olive} { ***FL: #1 }}}

@@

We have documented and analyzed a set of use cases related to software citation in \cite{SC-Use-Cases}.
Table~\ref{tab:use_cases} summarizes these use cases and makes clear what the requirements are for software citation in each case.
\katznote{not sure if this next long sentence should be here, should be in the table caption, or should be footnotes to the table, or even more than one of these}
\niemnote{Not sure either; definitely should include in the text due to length. Maybe an abbreviated version in the caption?}\flnote{If these ``definitions'' are not used anywhere else than in the table (and they don't really seem to be so far), then I tend towards putting this in the caption. That's where they are needed (in the table). I don't like footnotes for something like this.}
In the table,
``researcher'' includes both academic researchers (e.g., postdoc, tenure-track faculty member) and research software engineers;
``publisher'' includes both traditional publishers that publish text and\slash or software papers as well as archives such as Zenodo that directly publish software;
``reproduce'' can mean reproduction, replication, verification, validation, repeatability, and\slash or utility;
examples of indexers include Scopus, Web of Science, Google Scholar, and Microsoft Academic Search;
domain groups include bioCADDIE, CIG, etc.;
``repository'' refers to open-source software repositories such as ASCL, GitHub, Netlib, CRAN, institutional repositories;
``funder'' is a group that funds software or work using software; and
``UID'' means unique ID, such as DOI or PURL.
